Species motif participation provides unique information about species risk of extinction

### 2023-04-04 manuscript/JAE_reply.tex
git roundup and editing figure 6
Updates from Overleaf

@@

@@

>>>>

            \textbf{R:} Yes, a binomial error distribution would be more appropriate. We have corrected the error and updated our results accordingly and thank the Reviewer for pointing this out. [[something about what changed, if anything]]

@@

            \textbf{R:} [[This one might be have to be Anna's task - I can't get the ggplot2 code to run.]]

@@

                \textbf{R:} Probably the Reviewer is confused... I am confused by the comment.
